Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-03 latex/appendix.tex
tex

	\item [!] revise HM. align dap dan directly instead of the loss.

	\item [!] re-design Gradual Adversary for HM based on that for the amdsemi.

@@

@@

>>>>

	\item [*] re-design Gradual Adversary for HM based on that for the amdsemi. |
		\[
			(1-\frac{\text{prev\_loss}|_0^{2+\beta}}{2+\beta}) \times
			(\phi - H_\text{dst})\mathbb{I}\{\phi > H_\text{dst}\}
		\]
		So that for triplets that are not hard enoguh, when
		$prevloss \rightarrow 0$, $E[H_\text{dst}]\rightarrow \phi$.

@@

	\item [?] does the new generic HM work under FAT?

@@

	\item [\cmark] revise HM. align dap dan directly instead of the loss.
